---
title: "Gradients 4 Metabolomics Data analysis"
author: "Katherine Heal"
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
library(here)
print(here())
```

# TARGETED DATA PROCESSING
## QC of targeted data
Uses `QE_QC` function from here("analysis", "obi1_metabolomics", "functions", "targeted_dataprocessing_fxns.R")
Sources the raw Skyline files from here("data", "raw", "metabolomics", "rpom")
Writes out QC outputs into here("data", "intermediate", "metabolomics", "rpom", "targeted")
```{r, message=FALSE, error=FALSE, warning=FALSE}
# QC on all HILIC pos, HILIC neg, particulate and dissolved
source(here("analysis", "g4_metabolomics", "0101_targeted_QC.R"))
remove(list = ls())
```


## BMIS untargeted data
Perform BMIS normalization on HILIC particulate and dissolved samples
Uses `BMIS` function from here("analysis", "obi1_metabolomics", "functions", "targeted_dataprocessing_fxns.R")
Sources the dereplicated data from here("data", "intermediate", "metabolomics", "rpom", "targeted")
Writes out the BMISd data into here("data", "intermediate", "metabolomics", "rpom", "targeted")
```{r, message=FALSE, error=FALSE, warning=FALSE}
source(here("analysis", "g4_metabolomics", "0102_targeted_BMIS.R"))
remove(list = ls())
source(here("analysis", "g4_metabolomics", "0103_Dissolved_QC.R"))
remove(list = ls())
```


## Combine and tidy targeted data
Combines the BMISd targeted data from both HILIC particulate and dissolved samples and positive and negative
Writes out the combined and tidied data into here("data", "intermediate", "metabolomics", "rpom", "targeted")
```{r, message=FALSE, error=FALSE, warning=FALSE}
source(here("analysis", "g4_metabolomics", "0104_Combine_Tidy.R"))
remove(list = ls())
```


## Perform Enrichment calculations
