---
title: "Obi1 Metabolomics Data analysis"
author: "Katherine Heal"
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
library(here)
print(here())
```

# TARGETED DATA PROCESSING

## QC of targeted data
```{r, message=FALSE, error=FALSE, warning=FALSE}
# QC on all HILIC pos, HILIC neg, particulate and dissolved
source(here("analysis", "obi1_metabolomics", "0101_targeted_QC.R"))
remove(list = ls())
```

## BMIS targeted data
Perform BMIS normalization on HILIC particulate and dissolved samples
Also performs post-BMIS QC of targetted dissolved data
```{r, message=FALSE, error=FALSE, warning=FALSE}
source(here("analysis", "obi1_metabolomics", "0102_targeted_BMIS.R"))
remove(list = ls())
source(here("analysis", "obi1_metabolomics", "0103_Dissolved_QC.R"))
remove(list = ls())
```

## Combine and tidy data
```{r, message=FALSE, error=FALSE, warning=FALSE}
source(here("analysis", "obi1_metabolomics", "0104_Combine_Tidy.R"))
remove(list = ls())
```

# UNTARGETED DATA PROCESSING
## Dereplicate adducts from the MSdial output
```{r, message=FALSE, error=FALSE, warning=FALSE}
# QC on all HILIC pos, HILIC neg, particulate and dissolved
source(here("analysis", "obi1_metabolomics", "0201_MF_dereplication.R"))
remove(list = ls())
```

## BMIS untargeted data
Perform BMIS normalization on HILIC particulate and dissolved samples
```{r, message=FALSE, error=FALSE, warning=FALSE}
source(here("analysis", "obi1_metabolomics", "0202_untargeted_BMIS.R"))

remove(list = ls())
```

## Combine and tidy data
```{r, message=FALSE, error=FALSE, warning=FALSE}
source(here("analysis", "obi1_metabolomics", "0203_Combine_Tidy.R"))
remove(list = ls())
```




