---
title: "Obi1 Metabolomics Data analysis"
author: "Katherine Heal"
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
library(here)
print(here())
```


# Initial quality control of targeted data
```{r, message=FALSE, error=FALSE, warning=FALSE}
# QC on all HILIC pos, HILIC neg, particulate and dissolved
source(here("analysis", "obi1_metabolomics", "0101_targeted_QC.R"))
remove(list = ls())
```

# BMIS targeted data
Perform BMIS normalization on HILIC particulate and dissolved samples
Reran on 8/15/22, 8/18/22, 9/7/22
```{r}
source(here("01_targeted/0102_targeted_BMIS.R"))
remove(list = ls())
```

# post-BMIS QC of targetted dissolved data
Calculate batch-specific LODs for each analyte that made it through QC in dissolved.  Edit BMISd results if LOD > area for a specific compound
Reran on 8/15/22, 8/18/22, 9/7/22
```{r}
source("01_targeted/0103_Dissolved_QC.R")
remove(list = ls())
```

# Post-QC combine and tidy data
Reran on 8/15/22, 8/18/22, 9/7/22
```{r}
source("01_targeted/0104_Combine_Tidy.R")
remove(list = ls())
```

# Normalizing Obi1 by median fold change to explore 
Ran on 9/7/22
```{r}
#source("01_targeted/0105_Obi1_set1Part_norm.R")
#remove(list = ls())
```

# Making basic plots of the dissolved data to explore
Ran on 9/7/22
```{r}
#source("01_targeted/0106_Obi1_set1Diss.R")
#remove(list = ls())
```




