---
title: "Obi1 Metabolomics Data analysis"
author: "Katherine Heal"
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
library(here)
print(here())
```

# TARGETED DATA PROCESSING

## QC of targeted data
Uses `QE_QC` function from here("analysis", "obi1_metabolomics", "functions", "targeted_dataprocessing_fxns.R")
Sources the raw Skyline files from here("data", "raw", "metabolomics", "obi1")
Writes out QC outputs into here("data", "intermediate", "metabolomics", "obi1", "targeted")
```{r, message=FALSE, error=FALSE, warning=FALSE}
# QC on all HILIC pos, HILIC neg, particulate and dissolved
source(here("analysis", "obi1_metabolomics", "0101_targeted_QC.R"))
remove(list = ls())
```

## BMIS targeted data
Uses `BMIS` function from here("analysis", "obi1_metabolomics", "functions", "targeted_dataprocessing_fxns.R")
Perform BMIS normalization on HILIC particulate and dissolved samples
Also performs post-BMIS QC of targeted dissolved data
Sources QCd data from here("data", "intermediate", "metabolomics", "obi1", "targeted")
Writes BMIS checks into here("data", "intermediate", "metabolomics", "obi1", "targeted", "BMIS_checks")
Writes out BMIS outputs into here("data", "intermediate", "metabolomics", "obi1", "targeted")
```{r, message=FALSE, error=FALSE, warning=FALSE}
source(here("analysis", "obi1_metabolomics", "0102_targeted_BMIS.R"))
remove(list = ls())
source(here("analysis", "obi1_metabolomics", "0103_Dissolved_QC.R"))
remove(list = ls())
```

## Combine and tidy targeted data
Combines the BMISd targeted data from both HILIC particulate and dissolved samples and positive and negative
Writes out the combined and tidied data into here("data", "intermediate", "metabolomics", "obi1", "targeted")
```{r, message=FALSE, error=FALSE, warning=FALSE}
source(here("analysis", "obi1_metabolomics", "0104_Combine_Tidy.R"))
remove(list = ls())
```

# UNTARGETED DATA PROCESSING
## Dereplicate adducts from the MSdial output
Uses `dereplicate_MFs` function from here("analysis", "obi1_metabolomics", "functions", "untargeted_dataprocessing_fxns.R")
Sources the MSdial output from here("data", "raw", "metabolomics", "obi1", "untargeted")
Writes out the dereplicated data into here("data", "intermediate", "metabolomics", "obi1", "untargeted")
```{r, message=FALSE, error=FALSE, warning=FALSE}
# QC on all HILIC pos, HILIC neg, particulate and dissolved
source(here("analysis", "obi1_metabolomics", "0201_MF_dereplication.R"))
remove(list = ls())
```

## BMIS untargeted data
Perform BMIS normalization on HILIC particulate and dissolved samples
Uses `BMIS_MSdialoutput` function from here("analysis", "obi1_metabolomics", "functions", "untargeted_dataprocessing_fxns.R")
Sources the dereplicated data from here("data", "intermediate", "metabolomics", "obi1", "untargeted")
Writes out the BMISd data into here("data", "intermediate", "metabolomics", "obi1", "untargeted")
```{r, message=FALSE, error=FALSE, warning=FALSE}
source(here("analysis", "obi1_metabolomics", "0202_untargeted_BMIS.R"))
remove(list = ls())
```

## Combine and tidy untargeted data
Combines the BMISd untargeted data from both HILIC particulate and dissolved samples and positive and negative
Writes out the combined and tidied data into here("data", "intermediate", "metabolomics", "obi1", "untargeted")
```{r, message=FALSE, error=FALSE, warning=FALSE}
source(here("analysis", "obi1_metabolomics", "0203_Combine_Tidy.R"))
remove(list = ls())
```

# COMBINE TARGETED WITH UNTARGETED
## Dereplicate adducts from the MSdial output
Sources the combined and tidied targeted and untargeted data from here("data", "intermediate", "metabolomics", "obi1", "targeted") and here("data", "intermediate", "metabolomics", "obi1", "untargeted")
Also dereplicates the combined data so there are no targeted compounds in the untargeted data
Writes out the dereplicated data into here("data", "intermediate", "metabolomics", "obi1")
```{r, message=FALSE, error=FALSE, warning=FALSE}
source(here("analysis", "obi1_metabolomics", "0301_Combine_Tidy_TU.R"))
remove(list = ls())
```

## Do enrichment analysis
Sources the combined and dereplicated data from here("data", "intermediate", "metabolomics", "obi1")
Perform enrichment analysis on the data
Writes out the enrichment analysis into here("data", "intermediate", "metabolomics", "obi1")
```{r, message=FALSE, error=FALSE, warning=FALSE}
source(here("analysis", "obi1_metabolomics", "0302_EnrichmentCalcs.R"))
remove(list = ls())
```

# PLOTTING
## Fold change particulate plots
```{r, message=FALSE, error=FALSE, warning=FALSE}
source(here("analysis", "obi1_metabolomics", "0401_Plot_FC_particulate.R"))
remove(list = ls())
```

## Chromatograms
```{r, message=FALSE, error=FALSE, warning=FALSE}
source(here("analysis", "obi1_metabolomics", "0402_plot_MFchromats.R"))
remove(list = ls())
```

