---
title: "Rpom Metabolomics Data analysis"
author: "Katherine Heal"
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
library(here)
print(here())
```

# TARGETED DATA PROCESSING
## QC of targeted data
Uses `QE_QC` function from here("analysis", "obi1_metabolomics", "functions", "targeted_dataprocessing_fxns.R")
Sources the raw Skyline files from here("data", "raw", "metabolomics", "rpom")
Writes out QC outputs into here("data", "intermediate", "metabolomics", "rpom", "targeted")
```{r, message=FALSE, error=FALSE, warning=FALSE}
# QC on all HILIC pos, HILIC neg, particulate and dissolved
source(here("analysis", "rpom_metabolomics", "0101_targeted_QC.R"))
remove(list = ls())
```


## BMIS untargeted data
Perform BMIS normalization on HILIC particulate and dissolved samples
Uses `BMIS` function from here("analysis", "obi1_metabolomics", "functions", "targeted_dataprocessing_fxns.R")
Sources the dereplicated data from here("data", "intermediate", "metabolomics", "rpom", "targeted")
Writes out the BMISd data into here("data", "intermediate", "metabolomics", "rpom", "targeted")
```{r, message=FALSE, error=FALSE, warning=FALSE}
source(here("analysis", "rpom_metabolomics", "0102_targeted_BMIS.R"))
remove(list = ls())
```
